---
title: "EDA"
author: "Jiyan Jonas Schneider"
date: "12/24/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# EDA

This is the EDA for my project.
GOd R studio has become hard to use.. .


```{r cars}
library(arrow)
library(tidyverse)
theme_set(theme_gray(base_family="HiraginoSans-W3"))
```


```{r imports}

df  <- read_feather("../data/suumo23日.ar")

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
hist(df$apt_rent, breaks = 100)
```

We can see that our dataset has a very long right tail, which contains only very few observations.
These are rents per month. The author checked some of these outliers by hand, and they seem to be 
not mistakes in data input, but to be actual prices. 

When taking the log of the rents, the prices seem to move close to a "bell-shaped"
distribution, however nto necessarily normal. Furthermore, there are no negative prices, so the left
tail is shorter than the right tail.

```{r}
hist(log(df$apt_rent), breaks=100)

```
These are the prices of our rent. They look OK I think.. 

```{r}
```



```{r}
theme_dark(base_family = "HiraKakuProN-W3")


#+LATEX_HEADER: \setCJKmainfont{HiraginoSans-W0}

df %>% 
  group_by(station) %>% 
  count %>%
  arrange(-n) %>%
  head(25) %>% 
  arrange(-n) %>%
  ggplot(aes(y=reorder(station, n), x=n)) + geom_bar(stat="identity") + ylab("station") + xlab("Number of properties")

```

















